---
title: "Post-Scraper Run Diagnostics"
date: "`r format(Sys.time(), '%a %Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = F}
library(tidyverse)
library(kableExtra)
library(behindbarstools)
```

---

# Unsucessful Scrapers 

**Which scrapers didn't run successfully?**

The table below summarizes the scrapers that yielded errors and warnings. Highlighted rows yielded errors, meaning no data was extracted.

``` {r echo = F, warning = F}
# Read latest facility data 
new_df <- read_scrape_data(all_dates = FALSE)

# Get all log files from the latest run 
latest_date <- max(new_df$Date) %>% 
    as.character()
log_status <- behindbarstools::list_remote_data("log_files") %>% 
    str_subset(pattern = latest_date) %>% 
    as_tibble_col(column_name = "log") %>% 
    mutate(scraper = str_extract(log, "(?<=log_files/).*"))%>% 
    mutate(error = map(log, 
         ~read_file(.) %>% 
           str_detect(., "(?i)error")) %>%
           unlist()
           ) %>%
    mutate(status = ifelse(error, "ERROR", "WARN")) %>%
    mutate(error_on_date = map(log, 
           ~read_file(.) %>% 
             str_detect(., "(?i)Date is more than 30 different from expected")) %>%
             unlist()
             ) %>%
  select(-error)

# Highlight scrapers with errors   
kable(log_status %>% 
          select(-log), 
      col.names = c("Scraper", "Status", "Error on Date")) %>%     
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    row_spec(which(log_status$status == "ERROR"), background = "#ffa07a") %>% 
    scroll_box(height = "300px")
```

---

# Dashboard update frequency

**How many days has it been since we saw data updates from each scraped dashboard?** 

```{r update-frequency, echo = F, message = F, warning = F, fig.height = 10, fig.width = 15}
last_df <- pull_last_update()
last_df %>%
    filter(!is.na(days_late)) %>%
    # only get these kind of scrapers
    filter(jurisdiction %in% c("state", "federal", "immigration")) %>%
    # remove population scrapers here
    filter(!stringr::str_detect(id, "(?i)population")) %>%
    # remove youth scrapers here
    filter(!stringr::str_detect(id, "(?i)youth")) %>%
    # Do some renaming
    mutate(State = ifelse(jurisdiction == "immigration", "ICE", State)) %>%
    mutate(State = ifelse(jurisdiction == "federal", "BOP", State)) %>%
    # average across all scrapers for a given agency
    group_by(State) %>%
    summarize(days_late = mean(days_late), .groups = "drop") %>%
    mutate(State = forcats::fct_reorder(State, days_late)) %>%
    ggplot(aes(x = State, y = days_late, xend = State, yend = 0)) +
    geom_point(size = 3, color = "#D7790F") +
    geom_segment(size = 1.5, color = "#D7790F") +
    coord_flip() +
    theme_behindbars() +
    theme(
        panel.grid.major.y = element_blank(),
        axis.text.y = element_text(color = "#555526", size = 13),
        axis.text.x = element_text(color = "#555526", size = 18),
        panel.grid.major.x = element_line(
            color = "#92926C", linetype = "dotted"),
        axis.title.x = element_text(margin = margin(r = 20)),
        axis.title.y = element_blank(),
        legend.position = "none") +
    scale_color_bbdiscrete() +
    labs(x="", y="") +
    ggtitle(
        "Days Since Agency Updated Covid Data",
        stringr::str_c("As of ", as.character(first(last_df$Date))))
```

**How many scrapers were too old to scrape from (`error_on_date`)?** 

There were `r log_status %>% filter(error_on_date == TRUE) %>% nrow()` scrapers that errored on date. They were:

```{r error-on-date, echo = F, message = F, warning = F}
kable(log_status %>% 
          select(-log) %>%
          filter(error_on_date == TRUE),
      col.names = c("Scraper", "Status", "Error on Date")) %>%     
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    scroll_box(height = "300px")
```

---

# Comparison to Previous Run

## Aggregate Totals 

**How do the cumulative totals compare to the previous scraped data?** 

We expect all cumulative variables to increase with each subsequent scraper run. Rows highlighted below indicate that the aggregated total for a given variable fell in the latest scrape. This is based on totals from our scraped data in `adult_facility_covid_counts.csv`. 

``` {r check_previous, echo = F, message = F, warning = F}
# Read old facility data 
old_df <- stringr::str_c(
    "https://raw.githubusercontent.com/uclalawcovid19behindbars/data/master/", 
    "latest-data/latest_facility_counts.csv") %>% 
    read_csv()

covid_suffixes <- c(
  ".Confirmed", ".Deaths", ".Tadmin", ".Active", ".Initiated", ".Completed")

# Get totals 
rowAny <- function(x) rowSums(x) > 0

new_total <- new_df %>% 
    filter(rowAny(across(ends_with(covid_suffixes), ~ !is.na(.x)))) %>%
    select(all_of(ends_with(covid_suffixes))) %>%  
    summarise_all(sum_na_rm) %>% 
    pivot_longer(cols = everything(), 
                 names_to = "Variable", 
                 values_to = "New Total") 

old_total <- old_df %>% 
    select(all_of(ends_with(covid_suffixes))) %>% 
    summarise_all(sum_na_rm) %>% 
    pivot_longer(cols = everything(), 
                 names_to = "Variable", 
                 values_to = "Old Total")

joined <- full_join(old_total, new_total, by = "Variable") %>% 
    mutate(Difference = `New Total` - `Old Total`) %>% 
    mutate(cumulative_flag = ifelse(str_detect(Variable, ".Active|.Initiated|.Completed"), 0, 1))

# Highlight cumulative variables that decreased 
kable(joined %>% select(-cumulative_flag), format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    row_spec(which(joined$Difference < 0 & joined$cumulative_flag == 1), 
             background = "#ffa07a") %>% 
    scroll_box(height = "300px")
```

## By Facility

**Which facilities have metrics that are declining that shouldn't be?**

This is also based on totals from our scraped data in `adult_facility_covid_counts.csv` and includes facilities across all jurisdictions. Declining cumulative cases and deaths for incarcerated people are highlighted except from Texas, Ohio, and the BOP (where we know reported counts are not cumulative). 

``` {r check_previous_facility, echo = F, message = F, warning = F}
old_facility <- old_df %>% 
    filter(!is.na(Facility.ID)) %>% 
    filter(rowAny(across(ends_with(covid_suffixes), ~ !is.na(.x)))) %>%
    select(Facility.ID, State, Jurisdiction, Name, all_of(ends_with(covid_suffixes))) %>%  
    pivot_longer(cols = ends_with(covid_suffixes), 
                 names_to = "Variable", 
                 values_to = "Old Value")

new_facility <- new_df %>% 
    filter(!is.na(Facility.ID)) %>% 
    filter(rowAny(across(ends_with(covid_suffixes), ~ !is.na(.x)))) %>%
    select(Facility.ID, all_of(ends_with(covid_suffixes))) %>%  
    pivot_longer(cols = ends_with(covid_suffixes), 
                 names_to = "Variable", 
                 values_to = "New Value")

joined_facility <- full_join(old_facility, new_facility, 
                             by = c("Facility.ID", "Variable")) %>% 
    mutate(Difference = `New Value` - `Old Value`) %>% 
    filter(str_detect(Variable, ".Confirmed|.Deaths")) %>% 
    mutate(known_issues = ifelse(
        Jurisdiction == "federal" | State %in% c("Texas", "Ohio") & Jurisdiction == "state", 
        1, 0)) %>% 
    filter(Difference < 0) %>% 
    arrange(known_issues, Difference) %>% 
    select(-Facility.ID)

kable(joined_facility, format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    row_spec(which(joined_facility$Variable %in% c("Residents.Confirmed", "Residents.Deaths") 
                   & joined_facility$known_issues == 0), 
             background = "#ffa07a") %>% 
    scroll_box(height = "300px")
```

## By State 

**Which states have metrics that are declining that shouldn't be in aggregate?**

This compares to the state-aggregated totals in `state_aggregate_counts.csv` which excludes county jails and treats federal and immigration facilities as separate rows. 

```{r check_previous_state, echo = F, message = F, warning = F}
# Read latest statewide data 
new_state_df <- behindbarstools::calc_aggregate_counts(state = TRUE)

# Read old data 
old_state_df <- stringr::str_c(
    "https://raw.githubusercontent.com/uclalawcovid19behindbars/data/master/", 
    "latest-data/latest_state_counts.csv") %>% 
    read_csv()

measure_decline_df <- full_join(
    new_state_df %>%   
       filter(!is.na(Val)) %>%
        select(State, Measure, Val) %>% 
        rename("New Total" = "Val"), 
    
    old_state_df %>% 
        pivot_longer(-State, names_to = "Measure", values_to = "Old Total"), 
    
    by = c("State", "Measure")
    ) %>% 
    mutate(Difference = `New Total` - `Old Total`) %>% 
    filter(Difference < 0) %>% 
    filter(stringr::str_ends(
        Measure, ".Confirmed|.Deaths|.Tadmin|.Tested|.Initiated|.Completed"))

kable(measure_decline_df, format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Comparison to CPP 
``` {r, echo = F}
cpp_df <- read_cpp_data()

new_state_df %>% 
    left_join(cpp_df %>% 
                  select(-Date) %>% 
                  pivot_longer(!State, names_to = "Measure", values_to = "CPP"), 
              by = c("State", "Measure")) %>% 
    filter(!is.na(UCLA) & !is.na(CPP)) %>% 
    filter(str_detect(Measure, "Confirmed|Deaths")) %>% 
    mutate(diff = abs((UCLA - CPP) / CPP)) %>% 
    filter(diff != 0) %>% 
    arrange(desc(diff)) %>% 
    select(State, Measure, UCLA, CPP) %>% 
    kable(format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Comparison to AP/TMP

**How does our aggregated data compare to data from AP and the Marshall Project?** 

AP and the Marshall Project report [data on COVID in prisons at the state-level](https://www.themarshallproject.org/2020/05/01/a-state-by-state-look-at-coronavirus-in-prisons) each week. Because of differences in our methodology (e.g. data sources, update frequency, etc.), we do NOT expect our statewide totals to perfectly align with data from AP/TMP. The table below includes states where our totals differ by more than 20% OR where TMP is reporting values higher than we are. 

``` {r, echo = F}
new_state_df %>% 
    filter(!is.na(UCLA) & !is.na(MP)) %>% 
    filter(str_detect(Measure, "Confirmed|Deaths")) %>% 
    mutate(diff = abs((UCLA - MP) / MP)) %>% 
    filter(diff != 0) %>% 
    arrange(desc(diff)) %>% 
    select(State, Measure, UCLA, MP) %>% 
    kable(format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Recent Facility Increases 

## Cumulative Cases 

**Which facilities have seen the greatest increase in cumulative cases among incarcerated residents over the last 7 days?** 
``` {r, echo = F, fig.width = 15, fig.height = 7, warning = F}
scrape_df <- behindbarstools::read_scrape_data(all_dates = TRUE)

behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          plot_days = 30, 
                          num_fac = 3, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

## Active Cases 

**Which facilities have seen the greatest increase in active cases among incarcerated residents over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Residents.Active", 
                          plot_days = 30, 
                          num_fac = 3, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which facilities have seen the greatest increase in active cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Staff.Active", 
                          plot_days = 30, 
                          num_fac = 3, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which facilities have seen the greatest increase in cumulative cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Staff.Confirmed", 
                          plot_days = 30, 
                          num_fac = 3, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```


---

# New Facility Names 

**Were any new facility names scraped that will need to be added to the facility crosswalks?**

``` {r echo = F}
new_df %>% 
    filter(is.na(Facility.ID)) %>% 
    select(State, Name, Jurisdiction) %>% 
    arrange(State, Name) %>% 
    kable() %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Facilities with New Deaths 

**Which facilities had new deaths since the last scraper run?** 

``` {r echo = F}
# Get date of last scrape, and the previous scrape to compare it to 
date_last_scraped <- max(scrape_df$Date)
date_before_last_scrape <- max(scrape_df$Date[scrape_df$Date != max(scrape_df$Date)])

# Calculate change in deaths from previous date scraped
check <- scrape_df %>%
    filter(Date == date_last_scraped | Date == date_before_last_scrape) %>%
    group_by(Name, State, Jurisdiction) %>%
    mutate(previous_death_value = dplyr::lag(Residents.Deaths, order_by = Date)) %>%
    ungroup() %>%
    mutate(change_in_deaths = Residents.Deaths - previous_death_value,
           flag_change_deaths = ifelse(change_in_deaths != 0, TRUE, FALSE)) %>%
    arrange(-flag_change_deaths, -change_in_deaths)

check %>% 
    filter(change_in_deaths != 0) %>%
    select(State, Name, Residents.Deaths, previous_death_value, change_in_deaths) %>% 
    kable(col.names = c("State", "Name", "Current Deaths", "Previous Deaths", "Change")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```