---
title: "Post-Scraper Run Diagnostics"
date: "`r format(Sys.time(), '%a %Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = F}
library(tidyverse)
library(kableExtra)
library(behindbarstools)
#library(glue)
library(googlesheets4)
gs4_auth("ucla.law.covid.staff@gmail.com", scopes = "https://www.googleapis.com/auth/drive")
```

``` {r echo = F, warning = F, message = F}
# Read latest facility data 
new_df <- read_scrape_data(all_dates = FALSE)

# Get all log files from the latest run 
log_files <- behindbarstools::list_remote_data("log_files")

# Pull last update information
last_df <- pull_last_update()

# Read old facility counts for comparison to new_df (from read_scrape_data)
old_df <- stringr::str_c(
    "https://media.githubusercontent.com/media/uclalawcovid19behindbars/data/master/", 
    "latest-data/latest_facility_counts.csv") %>% 
    read_csv()

# Read old and new state aggregate counts for comparison
new_state_df <- calc_aggregate_counts(state = TRUE)

old_state_df <- stringr::str_c(
    "https://media.githubusercontent.com/media/uclalawcovid19behindbars/data/master/", 
    "latest-data/latest_state_counts.csv") %>% 
    read_csv()

# Read in CPP data
cpp_df <- behindbarstools::read_cpp_data()

# Read in historical state counts to plot highest increases in cumulative and active cases among staff and residents in last week
state_df <- read_csv("../data/historical-data/historical_state_counts.csv") %>%
  mutate(Name = State)

# Read in facility data for all dates to plot highest increases in cumulative and active cases among staff and residents in last week
scrape_df <- behindbarstools::read_scrape_data(all_dates = TRUE)
```

---

# Unsucessful Scrapers 

**Which scrapers didn't run successfully?**

The table below summarizes the scrapers that yielded errors and warnings. Highlighted rows yielded errors, meaning no data was extracted.

``` {r echo = F, warning = F}
latest_date <- unique(stringr::str_extract(log_files, "\\d+-\\d+-\\d+")) %>%
    as.Date() %>%
    max()

log_status <- log_files %>%
    str_subset(pattern = as.character(latest_date)) %>%
    as_tibble_col(column_name = "log") %>% 
    mutate(scraper = str_extract(log, "(?<=log_files/).*"))%>% 
    mutate(error = map(log, 
         ~read_file(.) %>% 
           str_detect(., "(?i)error")) %>%
           unlist()
           ) %>%
    mutate(status = ifelse(error, "ERROR", "WARN")) %>%
    mutate(error_on_date = map(log, 
           ~read_file(.) %>% 
             str_detect(., "(?i)Date is more than 30 different from expected")) %>%
             unlist()
             ) %>%
    select(-error)

# Highlight scrapers with errors   
kable(log_status %>% 
          select(-log), 
      col.names = c("Scraper", "Status", "Error on Date")) %>%     
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    row_spec(which(log_status$status == "ERROR"), background = "#ffa07a") %>% 
    scroll_box(height = "300px")
```

---

# Dashboard update frequency

**How many days has it been since we saw data updates from each scraped dashboard?** 

```{r update-frequency, echo = F, message = F, warning = F, fig.height = 10, fig.width = 15}
last_df %>%
    filter(!is.na(days_late)) %>%
    # only get these kind of scrapers
    filter(jurisdiction %in% c("state", "federal", "immigration")) %>%
    # remove population scrapers here
    filter(!stringr::str_detect(id, "(?i)population")) %>%
    # remove youth scrapers here
    filter(!stringr::str_detect(id, "(?i)youth")) %>%
    # Do some renaming
    mutate(State = ifelse(jurisdiction == "immigration", "ICE", State)) %>%
    mutate(State = ifelse(jurisdiction == "federal", "BOP", State)) %>%
    # average across all scrapers for a given agency
    group_by(State) %>%
    summarize(days_late = mean(days_late), .groups = "drop") %>%
    mutate(State = forcats::fct_reorder(State, days_late)) %>%
    ggplot(aes(x = State, y = days_late, xend = State, yend = 0)) +
    geom_point(size = 3, color = "#D7790F") +
    geom_segment(size = 1.5, color = "#D7790F") +
    coord_flip() +
    theme_behindbars() +
    theme(
        panel.grid.major.y = element_blank(),
        axis.text.y = element_text(color = "#555526", size = 13),
        axis.text.x = element_text(color = "#555526", size = 18),
        panel.grid.major.x = element_line(
            color = "#92926C", linetype = "dotted"),
        axis.title.x = element_text(margin = margin(r = 20)),
        axis.title.y = element_blank(),
        legend.position = "none") +
    scale_color_bbdiscrete() +
    labs(x="", y="") +
    ggtitle(
        "Days Since Agency Updated Covid Data",
        stringr::str_c("As of ", as.character(first(last_df$Date))))
```

**How many scrapers were too old to scrape from (`error_on_date`)?** 

There were `r log_status %>% filter(error_on_date == TRUE) %>% nrow()` scrapers that errored on date. They were:

```{r error-on-date, echo = F, message = F, warning = F}
kable(log_status %>% 
          select(-log) %>%
          filter(error_on_date == TRUE),
      col.names = c("Scraper", "Status", "Error on Date")) %>%     
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    scroll_box(height = "300px")
```

---

# Comparison to Previous Run

## Aggregate Totals 

**How do the cumulative totals compare to the previous scraped data?** 

We expect all cumulative variables to increase with each subsequent scraper run. Rows highlighted below indicate that the aggregated total for a given variable fell in the latest scrape.


## By Facility

**Which facilities have metrics that are declining that shouldn't be?**

This is based on totals from our scraped data in `adult_facility_covid_counts.csv` and includes facilities across all jurisdictions. Declining cumulative cases and deaths for incarcerated people are highlighted except from Texas, Ohio, and the BOP (where we know reported counts are not cumulative). 

``` {r check_previous_facility, echo = F, message = F, warning = F}
covid_suffixes <- c(
    ".Confirmed", ".Deaths", ".Tadmin", ".Active", ".Initiated", ".Completed")

rowAny <- function(x) rowSums(x) > 0

old_facility <- old_df %>% 
    filter(!is.na(Facility.ID)) %>% 
    filter(rowAny(across(ends_with(covid_suffixes), ~ !is.na(.x)))) %>%
    select(Facility.ID, State, Jurisdiction, Name, all_of(ends_with(covid_suffixes))) %>%  
    pivot_longer(cols = ends_with(covid_suffixes), 
                 names_to = "Variable", 
                 values_to = "Old Value")

new_facility <- new_df %>% 
    filter(!is.na(Facility.ID)) %>% 
    filter(rowAny(across(ends_with(covid_suffixes), ~ !is.na(.x)))) %>%
    select(Facility.ID, all_of(ends_with(covid_suffixes))) %>%  
    pivot_longer(cols = ends_with(covid_suffixes), 
                 names_to = "Variable", 
                 values_to = "New Value")

joined_facility <- full_join(old_facility, new_facility, 
                             by = c("Facility.ID", "Variable")) %>% 
    mutate(Difference = `New Value` - `Old Value`) %>% 
    filter(str_detect(Variable, ".Confirmed|.Deaths")) %>% 
    mutate(known_issues = ifelse(
        Jurisdiction == "federal" | State %in% c("Texas", "Ohio") & Jurisdiction == "state", 
        1, 0)) %>% 
    filter(Difference < 0) %>% 
    arrange(known_issues, Difference) %>% 
    select(-Facility.ID)

kable(joined_facility, format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    row_spec(which(joined_facility$Variable %in% c("Residents.Confirmed", "Residents.Deaths") 
                   & joined_facility$known_issues == 0), 
             background = "#ffa07a") %>% 
    scroll_box(height = "300px")
```

## By State 

**Which states have metrics that are declining that shouldn't be in aggregate?**

This compares to the state-aggregated totals in `state_aggregate_counts.csv` which excludes county jails and treats federal and immigration facilities as separate rows. 

```{r check_previous_state, echo = F, message = F, warning = F}

measure_decline_df <- full_join(
    new_state_df %>%   
       filter(!is.na(Val)) %>%
        select(State, Measure, Val) %>% 
        rename("New Total" = "Val"), 
    
    old_state_df %>% 
        pivot_longer(-State, names_to = "Measure", values_to = "Old Total"), 
    
    by = c("State", "Measure")
    ) %>% 
    mutate(Difference = `New Total` - `Old Total`) %>% 
    filter(Difference < 0) %>% 
    filter(stringr::str_ends(
        Measure, ".Confirmed|.Deaths|.Tadmin|.Tested|.Initiated|.Completed"))

kable(measure_decline_df, format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Comparison to CPP 
``` {r, echo = F}

new_state_df %>% 
    left_join(cpp_df %>% 
                  rename(Date.CPP = Date) %>% 
                  pivot_longer(!c(State, Date.CPP), names_to = "Measure", values_to = "CPP"), 
              by = c("State", "Measure")) %>% 
    filter(!is.na(UCLA) & !is.na(CPP)) %>% 
    filter(str_detect(Measure, "Confirmed|Deaths")) %>% 
    mutate(diff = abs((UCLA - CPP) / CPP)) %>% 
    filter(diff != 0) %>% 
    arrange(desc(diff)) %>% 
    select(State, Measure, UCLA, CPP, Date.UCLA, Date.CPP) %>% 
    kable(format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Recent Facility Increases 

## Cumulative Cases 

**Which facilities have seen the greatest increase in cumulative cases among incarcerated residents over the last 7 days?** 
``` {r, echo = F, fig.width = 15, fig.height = 7, warning = F}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

## Active Cases 

**Which facilities have seen the greatest increase in active cases among incarcerated residents over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Residents.Active", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which facilities have seen the greatest increase in active cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Staff.Active", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which facilities have seen the greatest increase in cumulative cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Staff.Confirmed", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

# Recent State Increases 

## Incarcerated people

**Which states have seen the greatest increase in cumulative cases among incarcerated residents over the last 7 days?** 
``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = state_df, 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which states have seen the greatest increase in active cases among incarcerated residents over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = state_df, 
                          metric = "Residents.Active", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

## Staff

**Which states have seen the greatest increase in active cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = state_df, 
                          metric = "Staff.Active", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

**Which states have seen the greatest increase in cumulative cases among staff over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
behindbarstools::plot_recent_fac_increases(scrape_df = state_df, 
                          metric = "Staff.Confirmed", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

---

# New Facility Names 

**Were any new facility names scraped that will need to be added to the facility crosswalks?**

``` {r echo = F}
new_df %>% 
    filter(is.na(Facility.ID)) %>% 
    filter(!Jurisdiction %in% c("psychiatric")) %>% 
    select(State, Name, Jurisdiction, Residents.Confirmed, Staff.Confirmed) %>% 
    arrange(State, Name) %>% 
    kable() %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```

---

# Facilities with New Deaths 

**Which facilities had new deaths since the last scraper run?** 

``` {r echo = F}
# Get date of last scrape, and the previous scrape to compare it to 
date_last_scraped <- max(scrape_df$Date)
date_before_last_scrape <- max(scrape_df$Date[scrape_df$Date != max(scrape_df$Date)])

# Calculate change in deaths from previous date scraped
check <- scrape_df %>%
    filter(Date == date_last_scraped | Date == date_before_last_scrape) %>%
    group_by(Name, State, Jurisdiction) %>%
    mutate(previous_death_value = dplyr::lag(Residents.Deaths, order_by = Date)) %>%
    ungroup() %>%
    mutate(change_in_deaths = Residents.Deaths - previous_death_value,
           flag_change_deaths = ifelse(change_in_deaths != 0, TRUE, FALSE)) %>%
    arrange(-flag_change_deaths, -change_in_deaths)

check %>% 
    filter(change_in_deaths != 0) %>%
    select(State, Name, Residents.Deaths, previous_death_value, change_in_deaths) %>% 
    kable(col.names = c("State", "Name", "Current Deaths", "Previous Deaths", "Change")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "300px")
```