---
title: "Post-Scraper Run Diagnostics"
date: "`r format(Sys.time(), '%a %Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include = F}
library(behindbarstools)
library(tidyverse)
library(googlesheets4)
library(kableExtra)
```

---

# Unsucessful Scrapers 

**Which scrapers didn't run successfully?**

The table below summarizes the scrapers that yielded errors and warnings. Highlighted rows yielded errors, meaning no data was extracted.

``` {r echo = F, warning = F}
# Read latest scraped data 
new_df <- read_scrape_data()

# Get all log files from the latest run 
latest_date <- max(new_df$Date) %>% 
    as.character()

log_status <- list_remote_data("log_files") %>% 
    str_subset(pattern = latest_date) %>% 
    as_tibble_col(column_name = "log") %>% 
    mutate(scraper = str_extract(log, "(?<=log_files/).*"))%>% 
    mutate(status = map(log, ~ read_file(.) %>% word(1)) %>% unlist()) 

# Highlight scrapers with errors   
kable(log_status %>% 
          select(-log), 
      col.names = c("Scraper", "Status")) %>%     
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    row_spec(which(log_status$status == "ERROR"), background = "#ffa07a") 
```

---

# Comparison to Previous Run

**How do the cumulative totals compare to the previous scraped data?** 

We expect all cumulative variables to increase with each subsequent scraper run. Rows highlighted below indicate that the aggregated total for a given variable fell in the latest scrape. The table compares data from the latest scrape to what is currently on [the Google Sheet](https://docs.google.com/spreadsheets/u/2/d/1X6uJkXXS-O6eePLxw2e4JeRtM41uPZ2eRcOA_HkPVTk/edit#gid=1641553906). 

``` {r check_previous, echo = F, message = F, warning = F}
# Read existing Google sheet data 
old_df <- "1X6uJkXXS-O6eePLxw2e4JeRtM41uPZ2eRcOA_HkPVTk" %>%
    read_sheet(sheet = 2, skip = 1) %>%
    .[2:nrow(.),] %>% 
    select(-Notes) %>% 
    setNames(names(new_df))

# Get totals 
new_total <- new_df %>% 
    select(Residents.Confirmed:Residents.Active) %>% 
    summarise_all(sum_na_rm) %>% 
    pivot_longer(cols = Residents.Confirmed:Residents.Active, 
                 names_to = "Variable", 
                 values_to = "New Total")

old_total <- old_df %>% 
    select(Residents.Confirmed:Residents.Active) %>% 
    summarise_all(sum_na_rm) %>% 
    pivot_longer(cols = Residents.Confirmed:Residents.Active, 
                 names_to = "Variable", 
                 values_to = "Old Total")

joined <- full_join(old_total, new_total, by = "Variable") %>% 
    mutate(Difference = `New Total` - `Old Total`) %>% 
    mutate(cumulative_flag = ifelse(str_detect(Variable, ".Active") 
                                  | str_detect(Variable, ".Pending")
                                  | str_detect(Variable, ".Quarantine"), 0, 1))

# Highlight cumulative variables that decreased 
kable(joined %>% select(-cumulative_flag), format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    column_spec(1, border_right = "1px solid #d2d2d2") %>% 
    row_spec(which(joined$Difference < 0 & joined$cumulative_flag == 1), background = "#ffa07a") 
```

## State by State: Metrics which are declining which shouldnt be

```{r check_previous, echo = F, message = F, warning = F}
measure_decline_df <- full_join(
  new_df %>%
    filter(Jurisdiction == "state") %>%
    select(
      State, Residents.Confirmed, Residents.Deaths, Residents.Tadmin,
      Staff.Confirmed, Staff.Deaths) %>%
    group_by(State) %>%
    summarise_all(sum_na_rm) %>%
    pivot_longer(-State, names_to = "Metric", values_to = "New"),
  
  old_df %>%
    filter(Jurisdiction == "state") %>%
    select(
      State, Residents.Confirmed, Residents.Deaths, Residents.Tadmin,
      Staff.Confirmed, Staff.Deaths) %>%
    group_by(State) %>%
    summarise_all(sum_na_rm) %>%
    pivot_longer(-State, names_to = "Metric", values_to = "Old")) %>%
  filter((New - Old) < 0)

kable(measure_decline_df, format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped"))
```

---

# Comparison to AP/TMP

**How does our aggregated data compare to data from AP and the Marshall Project?** 

AP and the Marshall Project report [data on COVID in prisons at the state-level](https://www.themarshallproject.org/2020/05/01/a-state-by-state-look-at-coronavirus-in-prisons) each week. Because of differences in our methodology (e.g. data sources, update frequency, etc.), we do NOT expect our statewide totals to perfectly align with data from AP/TMP. The table below highlights states where our totals differ by more than 20%. 

``` {r, echo = F}
# Read Marshall Project data 
mp_df <- "https://raw.githubusercontent.com/themarshallproject/COVID_prison_data/master/data/covid_prison_cases.csv" %>% 
    read.csv() %>% 
    mutate(Date = lubridate::mdy(as_of_date))

# Filter to latest data by date 
mp_total <- mp_df %>% 
    group_by(name) %>% 
    filter(Date == max(Date, na.rm = TRUE)) %>% 
    select(name, total_prisoner_cases, total_prisoner_deaths, total_staff_cases, total_staff_deaths) %>% 
    setNames(c("State", "Residents.Confirmed", "Residents.Deaths", "Staff.Confirmed", "Staff.Deaths")) 

# Restructure to match AP/TMP reporting 
# Only include state and federal facilities (not county jails and immigration detention centers)
# List federal as a separate state 
ucla_total <- new_df %>% 
    filter(Jurisdiction %in% c("state", "federal")) %>% 
    mutate(State = case_when(Jurisdiction == "federal" ~ "Federal", 
                             TRUE ~ State)) %>% 
    group_by(State) %>% 
    select(State, Residents.Confirmed, Residents.Deaths, Staff.Confirmed, Staff.Deaths) %>% 
    summarise_all(sum_na_rm) 
    
joined <- full_join(mp_total, ucla_total, 
                    by = "State", 
                    suffix = c(".MP", ".UCLA")) %>% 
    select(State, 
           Residents.Confirmed.MP, Residents.Confirmed.UCLA, 
           Residents.Deaths.MP,  Residents.Deaths.UCLA, 
           Staff.Confirmed.MP, Staff.Confirmed.UCLA, 
           Staff.Deaths.MP, Staff.Deaths.UCLA) %>% 
    janitor::adorn_totals("row") %>% 
    mutate(sort_ = ifelse(State == "Total", 1, 0)) %>% 
    mutate(Residents.Confirmed.Diff = abs((Residents.Confirmed.MP - Residents.Confirmed.UCLA) / Residents.Confirmed.UCLA), 
           Residents.Deaths.Diff = abs((Residents.Deaths.MP - Residents.Deaths.UCLA) / Residents.Deaths.UCLA), 
           Staff.Confirmed.Diff = abs((Staff.Confirmed.MP - Staff.Confirmed.UCLA) / Staff.Confirmed.UCLA),
           Staff.Deaths.Diff = abs((Staff.Deaths.MP - Staff.Deaths.UCLA) / Staff.Deaths.UCLA)) %>%  
    arrange(-sort_, State) %>% 
    select(-sort_)

# Highlight rows with differences above 20% 
kable(joined %>% 
          select(-ends_with(".Diff")), 
      col.names = c("State", "AP/TMP", "UCLA", "AP/TMP", "UCLA", "AP/TMP", "UCLA", "AP/TMP", "UCLA"), 
      format.args = list(big.mark = ",")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    add_header_above(c(" ", 
                       "Residents.Confirmed" = 2, 
                       "Residents.Deaths" = 2, 
                       "Staff.Confirmed" = 2,
                       "Staff.Deaths" = 2)) %>% 
    row_spec(which(joined$State == "Total"), bold = TRUE) %>% 
    row_spec(which(joined$Residents.Confirmed.Diff > 0.2
                 | joined$Residents.Deaths.Diff > 0.2 
                 | joined$Staff.Confirmed.Diff > 0.2
                 | joined$Staff.Deaths.Diff > 0.2), background = "#ffa07a") %>% 
    row_spec(0, align = "c") %>% 
    column_spec(c(1, 3, 5, 7), border_right = "1px solid #d2d2d2") 
```

---

# Recent Facility Increases 

## Cumulative Cases 

**Which facilities have seen the greatest increase in cumulative cases among incarcerated residents over the last 7 days?** 
``` {r, echo = F, fig.width = 15, fig.height = 7, warning = F}
scrape_df <- read_scrape_data(all_dates = TRUE, coalesce = TRUE)

plot_recent_fac_increases(scrape_df = scrape_df, 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

## Active Cases 

**Which facilities have seen the greatest increase in active cases among incarcerated residents over the last 7 days?**

``` {r, echo = F, fig.width = 15, fig.height = 7}
plot_recent_fac_increases(scrape_df = scrape_df, 
                          metric = "Residents.Active", 
                          plot_days = 30, 
                          num_fac = 5, 
                          auto_label = TRUE) + 
    labs(tag = "") 
```

---

# New Facility Names 

**Were any new facility names scraped that will need to be added to the facility crosswalks?**

``` {r echo = F}
new_df %>% 
    filter(is.na(Facility.ID)) %>% 
    select(State, Name, Jurisdiction) %>% 
    arrange(State, Name) %>% 
    kable() %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "250px")
```

---

# Facilities with New Deaths 

**Which facilities had new deaths since the last scraper run?** 

``` {r echo = F}
# Get date of last scrape, and the previous scrape to compare it to 
date_last_scraped <- max(scrape_df$Date)
date_before_last_scrape <- max(scrape_df$Date[scrape_df$Date != max(scrape_df$Date)])

# Calculate change in deaths from previous date scraped
check <- scrape_df %>%
    filter(Date == date_last_scraped | Date == date_before_last_scrape) %>%
    group_by(Name, State, Jurisdiction) %>%
    mutate(previous_death_value = dplyr::lag(Residents.Deaths, order_by = Date)) %>%
    ungroup() %>%
    mutate(change_in_deaths = Residents.Deaths - previous_death_value,
           flag_change_deaths = ifelse(change_in_deaths != 0, TRUE, FALSE)) %>%
    arrange(-flag_change_deaths, -change_in_deaths)

check %>% 
    filter(change_in_deaths != 0) %>%
    select(State, Name, Residents.Deaths, previous_death_value, change_in_deaths) %>% 
    kable(col.names = c("State", "Name", "Current Deaths", "Previous Deaths", "Change")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "250px")
```

---

# Decreasing Cumulative Counts 

## Cumulative Cases 

**Did any facilities see a decrease in cumulative cases?**

``` {r echo = F}
# Calculate change in cumulative cases from previous date scraped
check <- scrape_df %>%
    filter(Date == date_last_scraped | Date == date_before_last_scrape) %>%
    group_by(Name, State, Jurisdiction) %>%
    mutate(deaths_previous = dplyr::lag(Residents.Deaths, order_by = Date), 
           cases_previous = dplyr::lag(Residents.Confirmed, order_by = Date)) %>%
    ungroup() %>%
    mutate(deaths_diff = Residents.Deaths - deaths_previous,
           cases_diff = Residents.Confirmed - cases_previous, 
           deaths_neg_flag = ifelse(deaths_diff < 0, 1, 0), 
           cases_neg_flag = ifelse(cases_diff < 0, 1, 0))  

check %>% 
    filter(cases_neg_flag == 1) %>% 
    select(State, Name, Residents.Confirmed, cases_previous, cases_diff) %>% 
    arrange(cases_diff, State, Name) %>% 
    kable(col.names = c("State", "Name", "Current Cases", "Previous Cases", "Change")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "250px") 
```

## Cumulative Deaths 

**Did any facilities see a decrease in cumulative deaths?**

``` {r echo = F}
check %>% 
    filter(deaths_neg_flag == 1) %>% 
    select(State, Name, Residents.Deaths, deaths_previous, deaths_diff) %>% 
    arrange(deaths_diff, State, Name) %>% 
    kable(col.names = c("State", "Name", "Current Deaths", "Previous Deaths", "Change")) %>% 
    kable_styling(bootstrap_options = c("condensed", "striped")) %>% 
    scroll_box(height = "250px") 
```

---
