# Scraper diffs

```{r prison_data_sources, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)

translate_state <- function(x, reverse = FALSE){
    state_vec <- c(state.name, "DC")
    names(state_vec) <- c(state.abb, "DC")
    
    if(reverse){
        state_vec <- c(state.abb, "DC")
        names(state_vec) <- c(state.name, "DC")
    }
    
    state_vec[x]
}

facname_df <- "~/Documents/facility_data/data_sheets/fac_spellings.csv" %>%
    read_csv() %>%
    select(State, Name = facility_name_clean, Facility = facility_name_raw) %>%
    mutate(Name = str_to_upper(Name)) %>%
    unique()

ind_vars <- c("Date", "Name", "State")

new_df <-  list.files("../results/extracted_data", full.names = TRUE) %>%
    lapply(read_csv, col_types = cols()) %>%
    bind_rows() %>%
    select(-Resident.Deaths) %>%
    # remove values if they are missing a data name or state
    filter(!is.na(Date) & !is.na(Name) & State != "") %>%
    # order the names alphabetically
    select(!!sort(names(.))) %>%
    # put the indicator variables first
    select(!!ind_vars, !!(names(.)[!(names(.) %in% ind_vars)])) %>%
    mutate(Name = str_to_upper(Name)) %>%
    rename(Facility = Name) %>%
    mutate(State = translate_state(State)) %>%
    left_join(facname_df, by = c("Facility", "State")) %>%
    mutate(Name = ifelse(
        str_detect(Facility, "(?i)state-wide"), "STATEWIDE", Name))

old_df <-  "~/Downloads/UCLA Law Covid-19 Behind Bars Data Project " %>%
    str_c(
        "Professor Sharon Dolovich, Director - COVID-19 Jail_Prison ",
        "Confirmed Cases and Deaths.csv") %>%
    read_csv(skip = 1, col_types = cols()) %>%
    .[2:nrow(.),] %>%
    rename(Name = "County / Name of Facility") %>%
    select(
        Facility, Name, State,
        Rez.Con.Old = "Confirmed Cases \n(Residents)",
        Rez.Death.old = "Confirmed Deaths\n(Residents)")

compare_df <- old_df %>%
    full_join(
        new_df %>%
            filter(Date == lubridate::ymd("2020-10-30")) %>%
            select(Name, State, Residents.Confirmed, Residents.Deaths)) %>%
    arrange(State, Name)



```

## State level differences explained

```{r message=FALSE, warning=FALSE, echo=FALSE}

cont_df <- left_join(
    old_df %>%
        filter(Facility != "Federal Prison") %>%
        group_by(State) %>%
        summarise_if(is.numeric, sum, na.rm=T),
    
    new_df %>%
        filter(Date == lubridate::ymd("2020-10-30") & !is.na(State)) %>%
        select(State, Residents.Confirmed, Residents.Deaths) %>%
        group_by(State) %>%
        summarise(
            Residents.Confirmed = sum(Residents.Confirmed, na.rm = TRUE),
            Residents.Deaths = sum(Residents.Deaths, na.rm = TRUE)
        ), by = "State") %>%
    mutate(Residents.Confirmed = ifelse(
        is.na(Residents.Confirmed), 0, Residents.Confirmed)) %>%
    mutate(diff = abs(Residents.Confirmed - Rez.Con.Old)/Rez.Con.Old)

cont_df %>%
    mutate(group_diff = cut(diff, breaks = c(seq(0, 1, .05), 2), right = F)) %>%
    ggplot(aes(x=group_diff)) +
    geom_bar() +
    labs(
        x = "Percent Difference Between State Scrapers Confirmed Count",
        y="State Count") +
    theme_classic()
```

```{r message=FALSE, warning=FALSE, echo=FALSE}
cont_df %>%
    filter(diff > .05)
```

- Arkansas scraper broke new data is fixed and is the same level
- California missing LA jails infections and deaths
- Delaware, Maine, New Mexico, Rhode Island, Vermont, Wyoming need to add in manual data
- Idaho need to add in asymptomatic/current cases
- Louisiana, missing Orleans Parish Jails
- Missouri date mismatch
- New York missing jails for NYC
- OK stopped reporting data need to auto populate with past date (10-17-20)
- OR was double counting state-wide
- PA was missing Philly jail data
- SD time mismatch
- TN NA issue that has now been resolved
- TX was double county for state-wide now fixed
- UT day mismatch
- WI double counting state wide now fixed

# Detailed Examination not so important

```{r message=FALSE, warning=FALSE, echo=FALSE}

n_df <- left_join(
    old_df %>%
        filter(Facility != "Federal Prison") %>%
        group_by(State) %>%
        summarize(Nold = n()),
    
    new_df %>%
        filter(Date == lubridate::ymd("2020-10-30") & !is.na(State)) %>%
        group_by(State) %>%
        summarize(Nnew = n()), by = "State") %>%
    mutate(Nnew = ifelse(is.na(Nnew), 0, Nnew)) %>%
    mutate(diff = abs(Nnew - Nold)/Nold)

n_df %>%
    filter(diff != 0) %>%
    arrange(-diff)
```

- NE really only has state wide
- PA pop data needs to merge with other data
- AK is state wide only now
- MI resident and staff need to be harmonized
- TN resident and staff need to be harmonized
- CA staff data is missing

## alabama

Names are not currently being matched correctly but data looks on point

```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Alabama") %>%
    filter(!is.na(Rez.Co.Old))

new_df %>%
    filter(State == "Alabama" & Date == lubridate::ymd("2020-10-30")) %>%
    select(Facility, Residents.Confirmed, Residents.Deaths)
```

## alaska

```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Alaska")
```

## allegheny county
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(Name == "ALLEGHENY COUNTY JAIL")
```

## arizona & maricopa
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Arizona" & Facility != "Federal Prison")
```

## arkansas
Broke on 10/30 but looks good otherwise
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Arkansas" & Facility != "Federal Prison")

new_df %>%
    filter(State == "Arkansas" & Date == lubridate::ymd("2020-10-27"))
```
## California
need to add in LA jails resident numbers and names not matching
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "California" & Facility != "Federal Prison") %>%
    filter(!is.na(Rez.Co.Old))

compare_df %>%
    filter(State == "California") %>%
    #pull(Residents.Confirmed) %>%
    filter(!is.na(Residents.Confirmed))
```


## colorado
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Colorado" & Facility != "Federal Prison")
```

## conneticut
name not matching for a few
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Connecticut")
```

# Florida
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Florida")
```

# Georgia

```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Georgia")
```

# Hawaii
not all names matching
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Hawaii")
```

# Idaho
rez confirmed number was way off now adding in correct values
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Idaho")
```

# Illinois
rez confirmed number was way off now adding in correct values
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Illinois")
```

# Indiana
Numbers are mismatched because of slight day alignment mismatch
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Indiana")

new_df %>%
    filter(State == "Indiana" & Date == lubridate::ymd("2020-11-05")) %>%
    select(Facility, Residents.Confirmed, Residents.Deaths)
```

# Iowa
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Iowa")
```

# Kansas
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Kansas")
```


# Kentucky
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Kentucky")
```

# Kentucky
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Kentucky")
```

# Lousiana
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Louisiana")
```

# Missouri
name mismatches
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Missouri")

new_df %>%
        filter(Date == lubridate::ymd("2020-11-05") & State == "Missouri") %>%
        select(State, Residents.Confirmed, Residents.Deaths)
```

# New York
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "New York")
```

# Nebraska
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Nebraska")
```

# Oklahoma
```{r message=FALSE, warning=FALSE, echo=FALSE}
new_df %>%
    filter(Date == lubridate::ymd("2020-10-19") & State == "Oklahoma") %>%
    select(Residents.Confirmed, Residents.Deaths) %>%
    summarise_all(sum, na.rm=T)
```

# Pennsylvania
```{r message=FALSE, warning=FALSE, echo=FALSE}
new_df %>%
    filter(Date == lubridate::ymd("2020-10-30") & State == "Pennsylvania")
    
```

# South Dakota
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "South Dakota")
```

# Tennessee
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Tennessee")
```

# Utah
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Utah")

new_df %>%
    filter(State == "Utah" & Date == lubridate::ymd("2020-10-30"))
```

# West Virginia
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "West Virginia")
```

# Wisconsin
```{r message=FALSE, warning=FALSE, echo=FALSE}
compare_df %>%
    filter(State == "Wisconsin")
```